Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2018-12-01 ms.tex
added a figure for the GL dewar time series.

\subsection{GL Dewar Tests}

>>>>

\subsection{GL Dewar Tests}
At the University of Arizona, there is a laboratory setup for assessing NIRCam flight and spare detectors.
The key difference with the Asic dewar is that the detector readout electronics are completely different, using a Leach system that is operated outside of the dewar as opposed to the Asic, which is lives right next to the detectors.
The GL dewar detector stability tests are helpful in isolating noise sources that arise from the detectors versus the readout electronics.

\begin{figure*}
\gridline{\fig{ap_labels_S02illum_GLrun104.pdf}{0.32\textwidth}{Apertures}
		\fig{raw_tser_phot_S02illum_GLrun104.pdf}{0.32\textwidth}{Raw time series}
		\fig{refcor_phot_S02illum_GLrun104.pdf}{0.32\textwidth}{Ratio Time Series}}
\caption{The precision of this short-duration GL dewar test was the extremely high at $\sigma=$240 ppm after stabilization.
}\label{fig:GLtSeries}
\end{figure*}
